Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Fix line indenting

The softening lengths used in the simulations can affect the ability to
resolve the very thinnest planar structures, which in turn can affect how much
the density-based midplane varies as a function of azimuth. The Milky Way's
dense, star-forming gas disk is thought to have a scale height of about 40 pc (3--4 times the
cold gas softening length; \citealt{2019ApJ...871..145A}) and the thin stellar disk a scale height of about 300 pc (30 times the stellar softening length; \citealt{2008ApJ...673..864J}). We therefore expect that
resolution effects may still be affecting the scale heights of these
components in the simulations, especially the cold gas. Indeed, the stellar scale heights of
the simulated galaxies are equal to or larger than the MW's while the gas scale heights are significantly larger (although the proper basis comparison is less clear in the case of the gas; the quoted value for the Milky Way comes from studies of high-mass star-forming regions). As noted above, the midplanes defined by gas and stars can be tilted with respect to one another as well, precluding extending the precision of the gas midplane definition to the stellar component. In this
work we specifically consider azimuthal variations in the midplane \emph{as defined
by the stellar mass density}, which will subsequently be lower in the simulations than
in the MW: within 200 pc of the Sun the measured gas and stellar volume
densities in the MW are roughly comparable at $\sim .04\ \Msun\
\unit{pc}{-3}$, while in the simulations they are a factor of a few lower (see
Table 3 of \citealt{2018arXiv180610564S}). We thus expect that the degree of
midplane variation we find in the simulated systems is likely to be
\emph{less} than in the real MW, since on the smallest scales the simulations
are \emph{smoother} than the real Galaxy.

>>>>

The softening lengths used in the simulations can affect the ability to
resolve the very thinnest planar structures, which in turn can affect how much
the density-based midplane varies as a function of azimuth. The Milky Way's
dense, star-forming gas disk is thought to have a scale height of about $40\,\pc$
($3\text{-}4$ times the cold gas softening length; \citealt{2019ApJ...871..145A}) and
the thin stellar disk a scale height of about 300 pc (30 times the stellar
softening length; \citealt{2008ApJ...673..864J}). We therefore expect that
resolution effects may still be affecting the scale heights of these
components in the simulations, especially the cold gas. Indeed, the stellar
scale heights of the simulated galaxies are equal to or larger than the MW's
while the gas scale heights are significantly larger (although the proper
basis comparison is less clear in the case of the gas; the quoted value for
the Milky Way comes from studies of high-mass star-forming regions). As noted
above, the midplanes defined by gas and stars can be tilted with respect to
one another as well, precluding extending the precision of the gas midplane
definition to the stellar component. In this work we specifically consider
azimuthal variations in the midplane \emph{as defined by the stellar mass
density}, which will subsequently be lower in the simulations than in the MW:
within 200 pc of the Sun the measured gas and stellar volume densities in the
MW are roughly comparable at $\sim .04\ \Msun\
\unit{pc}{-3}$, while in the simulations they are a factor of a few lower (see
Table 3 of \citealt{2018arXiv180610564S}). We thus expect that the degree of
midplane variation we find in the simulated systems is likely to be
\emph{less} than in the real MW, since on the smallest scales the simulations
are \emph{smoother} than the real Galaxy.
